Market Simulator

### 2020-08-25 analysis/05_market_simulator.Rmd
Fixed some persona inputs to work with reactive element. Still need work on inputs that are scaled, perhaps make them discrete or dummys. Also fixed some of the persona beta levels to match persona inputs

beta_persona$levels = c("Intercept",
                        "Follow National News", 
                        "Follow International News",
                        "TV",
                        "Print",
                        "Online",
                        "Social Media",
                        "Radio",
                        "Email",
                        "Newsapp",
                        "Follow Government or Public Affairs", 
                        "No Travel to Developing Countries", 
                        "Political Preference", 
                        "Trust in Political Institutions",
                        "Others Should be Charitable",
                        "Worship Service Attendence",
                        "Religious Importance",
                        "Protestant",
                        "Christian Orthodox",
                        "Jewish",
                        "Muslim",
                        "Sikh",
                        "Hindu",
                        "Buddhist",
                        "Atheist",
                        "Other",
                        "Chartiy Trust Importance",
                        "Trust in Charity", 
                        "Donation Frequency", 
                        "Donation Amount",
                        "Volunteer 12 Months",
                        "Volunteer Frequence",
                        "Personal Activism",
                        "Family Activism",
                        "Religious Membership", 
                        "Sport or Recreational Membership", 
                        "Art, Music, or Educational Membership",
                        "Labor Union Membership",
                        "Political Party Membership",
                        "Environmental Organization Membership",
                        "Professional Association", 
                        "Humanitarian or Charity Membership",
                        "Consumer Organization Membership",
                        "Other Organization Membership",
                        "Female",
                        "Transgender",
                        "Prefer not to say",
                        "Other",
                        "Widowed",
                        "Divorced",
                        "Separated",
                        "Never Married",
                        "Education", 
                        "Income", 
                        "White", 
                        "Black", 
                        "American Indian", 
                        "Asian", 
                        "Pacific Islander", 
                        "Other", 
                        "Age")

@@

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "right")
    )
})

@@

# selectInput("model_choice",
#             label = "Select Model:",
#             choices = c("public_political_social_charity_demo"))

# sliderInput("p1_political_pref",
#        label = "Political Preference",
#        min = 0,
#        max = 7,
#        value = 0)

@@

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day' = 1,
                     'Every day' = 2,
                     "Once a week" = 3,
                     "Hardly ever" = 4,
                     "Never" = 5))

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"),
         multiple = TRUE)

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('Yes', 'No'))

selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("p1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other'))

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"))

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c("Yes", 'No' = "No Travel to Developing Countries"))

selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("p1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other'))

selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

@@

selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Yes", "No"))

selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other"))

@@

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))

selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("p1_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other'),
         multiple = TRUE)

selectInput("p1_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

selectInput("p2_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("p2_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p2_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"))

selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c('Yes', 'No'))

selectInput("p2_polical_pref",
         label = "Polical views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

selectInput("p2_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("p2_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other'))

selectInput("p2_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p2_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

@@

selectInput("p2_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Yes", "No"))

selectInput("p2_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

selectInput("p2_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

selectInput("p2_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

selectInput("p2_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other"))

@@

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))

selectInput("p2_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("p2_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other'),
         multiple = TRUE)

selectInput("p2_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

selectInput("p3_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

selectInput("p3_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p3_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online",
                     "Social Media",
                     "Radio",
                     "Email newsletters",
                     "News app"))

selectInput("p3_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p3_travel_developing",
         label = "Travel to developing country:",
         choices = c('Yes', 'No'))

selectInput("p3_polical_pref",
         label = "Polical views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p3_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p3_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

selectInput("p3_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

>>>>

beta_persona$levels = c("Intercept",
                        "Follow National News", 
                        "Follow International News",
                        "TV",
                        "Print",
                        "Online (excluding social media)",
                        "Social Media",
                        "Radio",
                        "Email",
                        "News app",
                        "Follow Government or Public Affairs", 
                        "Doesn't Travel", 
                        "Political Preference", 
                        "Trust in Political Institutions",
                        "Others Should be Charitable",
                        "Worship Service Attendence",
                        "Religious Importance",
                        "Protestant",
                        "Christian Orthodox",
                        "Jewish",
                        "Muslim",
                        "Sikh",
                        "Hindu",
                        "Buddhist",
                        "Atheist",
                        "Other (Religion)",
                        "Chartiy Trust Importance",
                        "Trust in Charity", 
                        "Donation Frequency", 
                        "Donation Amount",
                        "Not Volunteered",
                        "Volunteer Frequence",
                        "Personal Activism",
                        "Family Activism",
                        "Religious Membership", 
                        "Sport or Recreational Membership", 
                        "Art, Music, or Educational Membership",
                        "Labor Union Membership",
                        "Political Party Membership",
                        "Environmental Organization Membership",
                        "Professional Association", 
                        "Humanitarian or Charity Membership",
                        "Consumer Organization Membership",
                        "Other Organization Membership",
                        "Female",
                        "Transgender",
                        "Prefer not to say",
                        "Other (Gender)",
                        "Widowed",
                        "Divorced",
                        "Separated",
                        "Never Married",
                        "Education", 
                        "Income", 
                        "White", 
                        "Black", 
                        "American Indian", 
                        "Asian", 
                        "Pacific Islander", 
                        "Other (Race)", 
                        "Age")

@@

  ggplotly(df %>% filter(Type == "Market Share") %>%
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#006633", "#660000")) +
             theme(legend.position = "right")
    )
})

@@

@@

# Need to Fix
selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

# Need to Fix
selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p1_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("p1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'))

# Need to Fix
selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix

@@

# Need to Fix
selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Volunteered", "Not Volunteered"))

# Need to Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p1_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"))

@@

# Need to Fix
selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))
# Need to Fix
selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("p1_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

# Need to Fix
selectInput("p1_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

# Need to Fix
selectInput("p2_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

# Need to Fix
selectInput("p2_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p2_news_medium",
         label = "Medium to follow news:",
         choices = c("",
                     'TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p2_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p2_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))

selectInput("p2_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'))

# Need to Fix
selectInput("p2_charity_importance",
          label = "Charity Importance:",
          choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p2_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix

@@

# Need to Fix
selectInput("p2_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Volunteered", "Not Volunteered"))

# Need to Fix
selectInput("p2_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p2_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p2_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p2_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p2_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

selectInput("p2_gender",
         label = "Gender:",
         choices = c("Male",
                     "Female",
                     "Transgender",
                     "Prefer not to say",
                     "Other (Gender)"))

@@

# Need to Fix
selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))
# Need to Fix
selectInput("p2_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

selectInput("p2_race",
         label = "Race(s):",
         choices = c("",
                     'White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE)

# Need to Fix
selectInput("p2_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

# Need to Fix
selectInput("p3_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day',
                     'Every day',
                     "Once a week",
                     "Hardly ever",
                     "Never"))

# Need to Fix
selectInput("p3_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p3_news_medium",
         label = "Medium to follow news:",
         choices = c("",
                     'TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p3_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p3_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p3_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

# Need to Fix
selectInput("p3_worship_attendance",
         label = "Worship service attendance:",
         choices = c('Multiple times a week',
                     'Once a week',
                     "Once a month",
                     "Once a year",
                     "Never"))

# Need to Fix
selectInput("p3_religion_importance",
         label = "Importance of religion:",
         choices = c('Extremely important',
                     'Very important',
                     'Moderately important',
                     'Slightly important',
                     'Not at all important'))
